Cataclysmic variables are a key population of gravitational wave sources for LISA

### 2023-07-04 src/tex/ms.tex
Update abstract to fit 200 words

% Abstract of the paper
\begin{abstract}
AM~CVn stars are well established as an important population of gravitational wave (GW) sources for the planned \lisa\ mission. The less compact – but more numerous – cataclysmic variables (CVs), binaries containining white dwarfs which are observed to accrete hydrogen-rich material from a companion, have not been studied carefully in this context. Here, we estimate the predicted GW signals from the Galactic population of CVs and evaluate their significance for \lisa. First, we find that at least three known systems are expected to produce strong enough signals to be individually resolved within the first four years of \lisa's operation. Second, CVs will contribute significantly to the \lisa\ Galactic binary background, thus limiting the mission's sensitivity in the relevant frequency band. Third, we predict a spike in the unresolved GW background at a frequency corresponding to the CV minimum orbital period. This excess noise may impact the detection of other low signal-to-noise systems near this characteristic frequency. Fourth, we note that the amplitude and location of the excess noise spike associated with $P_{\rm{min}}\sim80~\mathrm{min}$ can be used to measure the CV space density and period bounce location with complementary and simple GW biases compared to the biases and selection effects that plague samples selected from electromagnetic signals. Our results highlight the need to explicitly include the Galactic CV population in the \lisa\ mission planning, both as individual GW sources and generators of background noise, as well as the exciting prospect of characterising the CV population through their GW emission.
\end{abstract}

>>>>

% Abstract of the paper
\begin{abstract}
The gravitational wave (GW) signals from the Galactic population of cataclysmic variables (CVs) has yet to be carefully assessed. Here we estimate these signals and evaluate their significance for \lisa. First, we find that at least three known systems are expected to produce strong enough signals to be individually resolved within the first four years of \lisa's operation. Second, CVs will contribute significantly to the \lisa\ Galactic binary background, limiting the mission's sensitivity in the relevant frequency band. Third, we predict a spike in the unresolved GW background at a frequency corresponding to the CV minimum orbital period. This excess noise may impact the detection of other systems near this characteristic frequency. Fourth, we note that the excess noise spike amplitude and location associated with $P_{\rm{min}}\sim80~\mathrm{min}$ can be used to measure the CV space density and period bounce location with complementary and simple GW biases compared to the biases and selection effects plaguing samples selected from electromagnetic signals. Our results highlight the need to explicitly include the Galactic CV population in the \lisa\ mission planning, both as individual GW sources and generators of background noise, as well as the exciting prospect of characterising the CV population through their GW emission.
\end{abstract}
